Performance-portable Parallel Programming in Computer Science Education with Kokkos

### 2020-02-10 src/0.Abstract.tex
Slit text into multiple files.
Fix a few typos
Minor changes. Added pdf output.

\begin{abstract}\label{chap:abstract}
Kokkos is a generic, performance-portable parallel programming model for host- and accelerator architectures in C++. It consists of a pure C++ interface, a specification and a programming library. The programming library exposes patterns and types and maps them to an underlying abstract machine model. 
This machine model offers a generic view of parallel hardware by abstracting from architecture- and vendor-specific programming models. In academia, this can contribute to a generic eduction of performance-portable parallel programming. In this work we present Kokkos from the perspective of educators, highlight key concepts and give an instruction to examples suited for incremental teaching of parallel programming in class.
\end{abstract}

>>>>

\begin{abstract}\label{chap:abstract}
Kokkos is a generic, performance-portable parallel programming model for host- and accelerator architectures in C++. It consists of a pure C++ interface, a specification and a programming library. The programming library exposes patterns and types and maps them to an underlying abstract machine model. This machine model offers a generic view of parallel hardware by abstracting from architecture- and vendor-specific programming models. In academia, this can contribute to a generic eduction of performance-portable parallel programming. In this work we present Kokkos from the perspective of educators, highlight key concepts and point the reader to examples and tutorials suited for incremental teaching of parallel programming in class.
\end{abstract}

### 2020-02-10 src/1.Introduction.tex
Minor changes. Added pdf output.

Teaching generic parallel programming today is difficult. Educators strive to balance considerations of architecture, programming model, and theoretical concepts. Unfortunately, not all architectures support all programming models, nor do many programming models offer enough abstractions to support modern hardware architectures sufficiently. Many vendor programming models compound this, requiring students to have access to specific hardware, and limiting the concepts of parallelism to those supported by that hardware.

@@

Kokkos\footnote{from Greek for grain or seed}~\cite{KOKKOS}, is a performance-portable, parallel programming model for C++ developed collaboratively by a number of national laboratories as part of the US Department of Energy Exascale Project\cite{ECP}. It consists of a programming model specification and a library. The specification defines execution and memory model and an application programming interface (library API). The runtime library exposes programming primitives, namelyexecution patterns and data structures which it maps to the underlying abstract machine model. The machine model creates a generic view of compute hardware and memories. The Kokkos library maps implements execution primitives on top of vendor-specific programming models, libraries, and memory layouts. Kokkos has been successfully used in many large-scale projects at SNL, University of Utah, Oak-Ridge National Laboratories, Los Alamos National Laboratories and others~\cite{KOKKOSPROJS}. We list its key properties as follows.

>>>>

Education of parallel programming today is difficult. Educators strive to balance considerations of architecture, programming model, and theoretical concepts. Unfortunately, not all architectures support all programming models, nor do many programming models offer enough abstractions to support modern hardware architectures sufficiently. Many vendor programming models compound this, requiring students to have access to specific hardware, and limiting the concepts of parallelism to those supported by that hardware.

@@

Kokkos\footnote{from Greek for grain or seed}~\cite{KOKKOS}, is a performance-portable, parallel programming model for C++ developed collaboratively by a number of national laboratories as part of the US Department of Energy Exascale Project\cite{ECP}. It consists of a programming model specification and a library. The specification defines execution and memory model and an application programming interface (library API). The runtime library exposes programming primitives, namely execution patterns and data structures which it maps to the underlying abstract machine model. The machine model creates a generic view of compute hardware and memories. The Kokkos library maps implements execution primitives on top of vendor-specific programming models, libraries, and memory layouts. Kokkos has been successfully used in many large-scale projects at SNL, University of Utah, Oak-Ridge National Laboratories, Los Alamos National Laboratories and others~\cite{KOKKOSPROJS}. We list its key properties as follows.
